Placeholder

### 2021-02-09 Paper_Histograms.Rmd
Reformatted the age retro graph in the gender, age, retro, ethnicity and employment figure

@@

@@

@@

@@

gridExtra::grid.arrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, nrow = 2)

>>>>

##Age gender and employ

@@

##Age gender and employ with gender labelled

@@

##Age gender employ and ethnicity

@@

```{r Tidy the age gender and employ graphs}

arranged_retro_age_plot <- dat.retro %>% 
  ggplot(aes(x = age_category_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Age (years)",
       y = "N participants") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank()) +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5))

@@

gridExtra::grid.arrange(arranged_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, nrow = 2)
